### 2023-09-12 3.Design/crossbar.tex
Changes to crossbar final figure + text change

%TODO understand better \subsection{Sneak path problem}
\subsection{Usage}
Since the analog system is only simulated in the inference phase of the \ac{NN}, the resistance doesn't need to change during this phase. The weights only change during the training phase, and the resistances are just a rendition of the weights (section TODO : ref weigths to res)

>>>>

%TODO understand better \subsection{Sneak path problem}
\subsection{Usage}
Since the analog system is only simulated in the inference phase of the \ac{NN}, the resistances don't need to change, the circuit used in the simulations are thus using resistors instead of memristors for the sake of simplicity (notably in generating the netlist of the system, TODO ref how hard it is to import parameters using spice netlists). The weights only change during the training phase, and the resistances are just a rendition of the weights (TODO : ref weigths to res).
